---
title: "Join Assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(xml2)
```


This chapter is about Joins.
WE load Tennis data in order to analysis this dataset;
```{r}
tennis_data <- load("~/atp_tennis_data_2017.RData")
```


### 1-Rank countries (flag cides) by the number of singles champions
We join two dataframes with player_id and singles_winner_player_id coloumns in order to get winner players. 
```{r}
tennis_lj<-left_join(tourney_df, player_df,by = c("singles_winner_player_id"="player_id"))
```

First solution of this one:
```{r cars}
tennis_lj_sum <-
  tennis_lj %>%
  count(flag_code,sort=TRUE)
```

Other solution of this one:
```{r}
tennis_lj_sum <-
  tennis_lj %>%
  group_by(flag_code) %>%
  summarise(total_win = n()) %>%
  arrange(desc(total_win))
```

### 2-Rank countries which did not get any singles championships by the games won when they win the match
In this analysis we have to find the non-champion players using anti-join
```{r}
nonchamp_players <-
  player_df %>% select(player_id,flag_code)%>% anti_join(.,tennis_lj_sum)
```

So the Data set ready we now have to write the SQL in order to fulfill the reqirement.
```{r}
nonchamp_players %>% left_join(.,score_df,by=c("player_id"="winner_player_id")) %>%
  group_by(flag_code) %>% summarise(total_won=sum(winner_games_won,na.rm=TRUE)) %>%arrange(desc(total_won))
```

### 3-Final Winners
```{r}
final_winners <-
  inner_join(player_df,score_df,by=c("player_id"="winner_player_id")) %>%
  filter(tourney_round_name=="Finals") %>%
  group_by(player_slug) %>%
  summarise(final_count = n()) %>%
  arrange(desc(final_count))

final_winners
```

### 4-Final Losers 
```{r}
final_losers <- 
  inner_join(player_df,score_df,by=c("player_id"="loser_player_id")) %>%
  filter(tourney_round_name=="Finals") %>%
  group_by(player_slug) %>%
  summarise(final_count = n()) %>%
  arrange(desc(final_count))

final_losers
```

### 5-Most Final Played Players
I merge the Final winners and final losers datasets to analysis the Most Final Played Players.  
```{r}
merge_losers_winners <-
rbind(final_losers,final_winners)

merge_losers_winners%>%
  group_by(player_slug) %>%
  summarise(total_finals=sum(final_count,na.rm=TRUE)) %>%
  arrange(desc(total_finals))  
```

